A Cloud Native Approach to Adversarial Robustness of Neural Networks

### 2024-03-29 main.tex

\subsection{AFR Models}
\label{res:afr}
Table~\ref{tab:Combined} shows the performance metrics for all three AFR models, as outlined in Sec.~\ref{survival_time}. It shows that the aft models using Weibull, log-logistic and log-normal functions have similar predictive abilities, but we used the log-logistic model to render partial effect due to its marginally improved AIC.
\input{plots/combined/aft_comparison}

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{\linewidth}
        \includegraphics[width=.8\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
        \caption{Batch Size Partial Effect}
    \end{subfigure}
    \begin{subfigure}[b]{\linewidth}
        \includegraphics[width=.8\linewidth,clip]{plots/combined/log_logistic_aft.pdf}
        \caption{Coefficients of the Covariates}
    \end{subfigure}
    \begin{subfigure}[b]{\linewidth}
        \includegraphics[width=.8\linewidth,clip]{plots/combined/log_logistic_attack_eps_partial_effect.pdf}
        \caption{Partial Effect  of $\varepsilon$ of $S(t)$ }
    \end{subfigure}
    \caption{This shows the partial effects plots for}
\end{figure}

\subsection{Comparative Risk}
\cm{TODO}
Call back to the comparative risk and the fast rejection mechanism.

>>>>

\subsection{AFR Models}
\label{res:afr}
Table~\ref{tab:combined} shows the performance metrics for all three AFR models, as outlined in Sec.~\ref{survival_time}. It shows that the aft models using Weibull, log-logistic and log-normal functions have similar predictive abilities, but we used the log-logistic model to render partial effect due to its marginally improved AIC.
\input{plots/combined/aft_comparison}

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{\linewidth}
        \centering
        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
        \caption{Plot depicting the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis).}
    \end{subfigure}
    \begin{subfigure}[b]{\linewidth}
        \centering
        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_aft.pdf}
        \caption{Coefficients of the Covariates for the Log Logistic AFR model}
    \end{subfigure}
    \begin{subfigure}[b]{\linewidth}
        \centering
        \includegraphics[width=.7\linewidth,clip]{plots/combined/log_logistic_attack_eps_partial_effect.pdf}
        \caption{Partial Effect  of $\varepsilon$ of $S(t)$ }
    \end{subfigure}
    \caption{This shows the partial effects plots for}
\end{figure}
